Codebook created on 2024-02-27 at 2024-02-27 16:22:04.046895

### 2024-02-28 Data/AnalysisData/codebook_data_H2.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:42.481222"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 3 variables.

>>>>

---
title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:07.480565"
output: github_document
---

@@

## Dataset description
The data contains 670 cases and 9 variables.

### 2024-02-28 Data/AnalysisData/codebook_data_H3_avg.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:45.103283"
output: github_document
---

@@

## Dataset description
The data contains 18 cases and 3 variables.

>>>>

---
title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:10.406518"
output: github_document
---

@@

## Dataset description
The data contains 19 cases and 9 variables.

### 2024-02-28 Data/AnalysisData/codebook_data_H3_multiple.Rmd
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2023-11-09 at 2023-11-09 13:46:43.923892"
output: github_document
---

@@

## Dataset description
The data contains 713 cases and 4 variables.

>>>>

---
title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:09.116352"
output: github_document
---

@@

## Dataset description
The data contains 670 cases and 10 variables.

### 2024-02-28 Data/AnalysisData/codebook_plot_23_data_alpha.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:58.540839"
output: github_document
---

@@

## Dataset description
The data contains 658 cases and 5 variables.

>>>>

---
title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:12.063393"
output: github_document
---

@@

## Dataset description
The data contains 669 cases and 11 variables.

### 2024-02-28 Data/AnalysisData/codebook_plot_23_data_omega.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:59:02.156609"
output: github_document
---

@@

## Dataset description
The data contains 558 cases and 5 variables.

>>>>

---
title: "Codebook created on 2024-02-26 at 2024-02-26 14:50:13.488761"
output: github_document
---

@@

## Dataset description
The data contains 515 cases and 11 variables.

### 2024-02-28 Data/AnalysisData/codebook_plot_23_data_reported_alpha.Rmd
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2024-02-14 at 2024-02-14 09:47:30.71879"
output: github_document
---

@@

## Dataset description
The data contains 9 cases and 4 variables.

>>>>

---
title: "Codebook created on 2024-02-26 at 2024-02-26 16:01:29.661356"
output: github_document
---

@@

## Dataset description
The data contains 9 cases and 7 variables.

### 2024-02-28 Data/AnalysisData/codebook_plot_456_data.Rmd
failed attempt to include R results as numbers in text.
added the replicability and reliability test table.
added the results for H5 and H6, including plot 46, which also required the adition of the plot_46_data_rev file, which lead to a rerun of the final data creation code.
Opened up the Many Labs retrieved data for the project.
starting to restructure the article based on feedback. Start on adding meta-analysis component to H2
changed plot456 and plot46, and first stages of restructuring results.

---
title: "Codebook created on 2023-11-07 at 2023-11-07 11:58:44.141596"
output: github_document
---

@@

## Dataset description
The data contains 924 cases and 3 variables.

>>>>

---
title: "Codebook created on 2024-02-27 at 2024-02-27 16:22:04.046895"
output: github_document
---

@@

## Dataset description
The data contains 924 cases and 4 variables.
